Analytical choices for analyzing multidimensional behavior - Many analysts test hypotheses about human speech.

### 2021-03-18 RR_manuscript/Draft_RR.tex
:memo: - render RR

As a second step, we will investigate (a) the extent to which the individual standardized effect sizes are affected by a series of predictors related to analytical and demographic factors (see below); and (b) the extent to which deviations from the meta-analytic estimate by the individual standardized effect sizes relate to those same predictors.
We will fit two Bayesian regression models, one for (a) and one for (b).

\textbf{Analytical factors}. We will estimate the influence of the following predictors related to the analytical characteristics of each team's reported analysis:

@@

\textbf{Demographic factors}. We will include the following demographic factors about the teams:

@@

\textbf{Models specification}. The models for (a) and (b) from above will be fitted as measurement-error models, both with the same predictors as detailed in the preceding paragraphs.
The outcome variable of model (a) will be the standardized effect sizes, while that of model (b) the deviation of these from the meta-analytical effect size.
The deviation of the standardized effects will be calculated as the difference of the standardized effect sizes from the meta-analytical point estimate.
The measure of uncertainty of the effect deviation will be calculated as the joint standard deviation by taking the square root of the joint variance \(Var(\eta_i) + Var(\hat{\eta}) + 2Cov(\eta_i, \hat{\eta})\).

>>>>

As a second step, we will investigate the extent to which the individual standardized effect sizes are affected by a series of predictors related to analytical and researcher-related factors.

\textbf{Analytical predictors}. We will estimate the influence of the following predictors related to the analytical characteristics of each team's reported analysis:

@@

\textbf{Researcher-related factors}. We will include the following predictors about the teams:

@@

\textbf{Model specification}. The model will be fitted as measurement-error models, with the predictors detailed in the preceding paragraphs.
The outcome variable of the model will be the standardized effect sizes.
